Summary of Performance Measures for Scenario OR

### 2024-08-21 doc/performanceER.Rmd
performance for all 3 scenarios

---
title: "Summary of Performance Measures for Normal Scenario"
author: "Ehsan, Yang"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
  pdf_document:
    toc: true
    toc_depth: 2
---

@@

load("results/scenario/bross.RData")
load("results/scenario/hybrid.RData")
load("results/scenario/lasso.RData")
load("results/scenario/enet.RData")
load("results/scenario/ga.RData")
load("results/scenario/xgboost.RData")
load("results/scenario/rf.RData")
load("results/scenario/forward.RData")
load("results/scenario/backward.RData")

@@

unique(ss1$summ$stat)
autoplot(s1, type = "lolly", stats = "nsim")+ custom_theme
autoplot(s1, type = "lolly", stats = "bias")+ custom_theme  + labs(x = "Bias")
ggsave(filename = "images/scenario/bias.png")
autoplot(s1, type = "lolly", stats = "relerror")+ custom_theme  + labs(x = "Relative % error")
autoplot(s1, type = "lolly", stats = "cover")+ custom_theme  + labs(x = "95% coverage")
ggsave(filename = "images/scenario/cover.png")
autoplot(s1, type = "lolly", stats = "becover")+ custom_theme  + labs(x = "95% bias-eliminated coverage")
ggsave(filename = "images/scenario/becover.png")
autoplot(s1, type = "lolly", stats = "modelse")+ custom_theme + labs(x = "Model SE")
ggsave(filename = "images/scenario/modelse.png")
autoplot(s1, type = "lolly", stats = "empse")+ custom_theme  + labs(x = "Empirical SE")
ggsave(filename = "images/scenario/empse.png")
autoplot(s1, type = "lolly", stats = "mse")+ custom_theme + labs(x = "MSE")
autoplot(s1, type = "lolly", stats = "relprec")+ custom_theme
autoplot(s1, type = "lolly", stats = "power")+ custom_theme
zip_plot <- autoplot(s1, type = "zip", zoom = 0.5) + custom_theme
dashed_line <- geom_hline(yintercept = 0.95, linetype = "dashed", color = "blue")
zip_plot + 
  annotate("segment", x = -Inf, xend = Inf, y = 0.95, yend = 0.95, linetype = "dashed", color = "blue") +
  dashed_line
ggsave(filename = "images/scenario/zip.png")
```

@@

ggplot(melted_data, aes(x = model, y = value, fill = factor(variable, levels = c("empse", "modelse")))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  coord_flip() + # Makes the bar plots horizontal
  labs(y = "SE", x = "model", fill = "SE") +
  scale_fill_manual(
    values = c("empse" = "lightgray", "modelse" = "darkgray"), 
    labels = c("empse" = "Empirical SE", "modelse" = "Model SE")
  ) +
  custom_theme
ggsave(filename = "images/scenario/secompare.png")
```

>>>>

---
title: "Summary of Performance Measures for Scenario ER"
author: "Ehsan, Yang"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
  pdf_document:
    toc: true
    toc_depth: 2
---

@@

load("results/scenarioER/bross.RData")
load("results/scenarioER/hybrid.RData")
load("results/scenarioER/lasso.RData")
load("results/scenarioER/enet.RData")
load("results/scenarioER/ga.RData")
load("results/scenarioER/xgboost.RData")
load("results/scenarioER/rf.RData")
load("results/scenarioER/forward.RData")
load("results/scenarioER/backward.RData")

@@

unique(ss1$summ$stat)
autoplot(s1, type = "lolly", stats = "nsim")+ custom_theme
autoplot(s1, type = "lolly", stats = "bias")+ custom_theme  + labs(x = "Bias")
ggsave(filename = "images/scenarioER/bias.png")
autoplot(s1, type = "lolly", stats = "relerror")+ custom_theme  + labs(x = "Relative % error")
autoplot(s1, type = "lolly", stats = "cover")+ custom_theme  + labs(x = "95% coverage")
ggsave(filename = "images/scenarioER/cover.png")
autoplot(s1, type = "lolly", stats = "becover")+ custom_theme  + labs(x = "95% bias-eliminated coverage")
ggsave(filename = "images/scenarioER/becover.png")
autoplot(s1, type = "lolly", stats = "modelse")+ custom_theme + labs(x = "Model SE")
ggsave(filename = "images/scenarioER/modelse.png")
autoplot(s1, type = "lolly", stats = "empse")+ custom_theme  + labs(x = "Empirical SE")
ggsave(filename = "images/scenarioER/empse.png")
autoplot(s1, type = "lolly", stats = "mse")+ custom_theme + labs(x = "MSE")
autoplot(s1, type = "lolly", stats = "relprec")+ custom_theme
autoplot(s1, type = "lolly", stats = "power")+ custom_theme
zip_plot <- autoplot(s1, type = "zip", zoom = 0.5) + custom_theme
dashed_line <- geom_hline(yintercept = 0.95, linetype = "dashed", color = "blue")
zip_plot + 
  annotate("segment", x = -Inf, xend = Inf, y = 0.95, yend = 0.95, linetype = "dashed", color = "blue") +
  dashed_line
ggsave(filename = "images/scenarioER/zip.png")
```

@@

ggplot(melted_data, aes(x = model, y = value, fill = factor(variable, levels = c("empse", "modelse")))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  coord_flip() + # Makes the bar plots horizontal
  labs(y = "SE", x = "model", fill = "SE") +
  scale_fill_manual(
    values = c("empse" = "lightgray", "modelse" = "darkgray"), 
    labels = c("empse" = "Empirical SE", "modelse" = "Model SE")
  ) +
  custom_theme
ggsave(filename = "images/scenarioER/secompare.png")
```

### 2024-08-21 doc/performanceOR.Rmd
performance for all 3 scenarios

---
title: "Summary of Performance Measures for Scenario ER"
author: "Ehsan, Yang"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
  pdf_document:
    toc: true
    toc_depth: 2
---

@@

load("results/scenarioER/bross.RData")
load("results/scenarioER/hybrid.RData")
load("results/scenarioER/lasso.RData")
load("results/scenarioER/enet.RData")
load("results/scenarioER/ga.RData")
load("results/scenarioER/xgboost.RData")
load("results/scenarioER/rf.RData")
load("results/scenarioER/forward.RData")
load("results/scenarioER/backward.RData")

@@

unique(ss1$summ$stat)
autoplot(s1, type = "lolly", stats = "nsim")+ custom_theme
autoplot(s1, type = "lolly", stats = "bias")+ custom_theme  + labs(x = "Bias")
ggsave(filename = "images/scenarioER/bias.png")
autoplot(s1, type = "lolly", stats = "relerror")+ custom_theme  + labs(x = "Relative % error")
autoplot(s1, type = "lolly", stats = "cover")+ custom_theme  + labs(x = "95% coverage")
ggsave(filename = "images/scenarioER/cover.png")
autoplot(s1, type = "lolly", stats = "becover")+ custom_theme  + labs(x = "95% bias-eliminated coverage")
ggsave(filename = "images/scenarioER/becover.png")
autoplot(s1, type = "lolly", stats = "modelse")+ custom_theme + labs(x = "Model SE")
ggsave(filename = "images/scenarioER/modelse.png")
autoplot(s1, type = "lolly", stats = "empse")+ custom_theme  + labs(x = "Empirical SE")
ggsave(filename = "images/scenarioER/empse.png")
autoplot(s1, type = "lolly", stats = "mse")+ custom_theme + labs(x = "MSE")
autoplot(s1, type = "lolly", stats = "relprec")+ custom_theme
autoplot(s1, type = "lolly", stats = "power")+ custom_theme
zip_plot <- autoplot(s1, type = "zip", zoom = 0.5) + custom_theme
dashed_line <- geom_hline(yintercept = 0.95, linetype = "dashed", color = "blue")
zip_plot + 
  annotate("segment", x = -Inf, xend = Inf, y = 0.95, yend = 0.95, linetype = "dashed", color = "blue") +
  dashed_line
ggsave(filename = "images/scenarioER/zip.png")
```

@@

ggplot(melted_data, aes(x = model, y = value, fill = factor(variable, levels = c("empse", "modelse")))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  coord_flip() + # Makes the bar plots horizontal
  labs(y = "SE", x = "model", fill = "SE") +
  scale_fill_manual(
    values = c("empse" = "lightgray", "modelse" = "darkgray"), 
    labels = c("empse" = "Empirical SE", "modelse" = "Model SE")
  ) +
  custom_theme
ggsave(filename = "images/scenarioER/secompare.png")
```

>>>>

---
title: "Summary of Performance Measures for Scenario OR"
author: "Ehsan, Yang"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
  pdf_document:
    toc: true
    toc_depth: 2
---

@@

load("results/scenarioOR/bross.RData")
load("results/scenarioOR/hybrid.RData")
load("results/scenarioOR/lasso.RData")
load("results/scenarioOR/enet.RData")
load("results/scenarioOR/ga.RData")
load("results/scenarioOR/xgboost.RData")
load("results/scenarioOR/rf.RData")
load("results/scenarioOR/forward.RData")
load("results/scenarioOR/backward.RData")

@@

unique(ss1$summ$stat)
autoplot(s1, type = "lolly", stats = "nsim")+ custom_theme
autoplot(s1, type = "lolly", stats = "bias")+ custom_theme  + labs(x = "Bias")
ggsave(filename = "images/scenarioOR/bias.png")
autoplot(s1, type = "lolly", stats = "relerror")+ custom_theme  + labs(x = "Relative % error")
autoplot(s1, type = "lolly", stats = "cover")+ custom_theme  + labs(x = "95% coverage")
ggsave(filename = "images/scenarioOR/cover.png")
autoplot(s1, type = "lolly", stats = "becover")+ custom_theme  + labs(x = "95% bias-eliminated coverage")
ggsave(filename = "images/scenarioOR/becover.png")
autoplot(s1, type = "lolly", stats = "modelse")+ custom_theme + labs(x = "Model SE")
ggsave(filename = "images/scenarioOR/modelse.png")
autoplot(s1, type = "lolly", stats = "empse")+ custom_theme  + labs(x = "Empirical SE")
ggsave(filename = "images/scenarioOR/empse.png")
autoplot(s1, type = "lolly", stats = "mse")+ custom_theme + labs(x = "MSE")
autoplot(s1, type = "lolly", stats = "relprec")+ custom_theme
autoplot(s1, type = "lolly", stats = "power")+ custom_theme
zip_plot <- autoplot(s1, type = "zip", zoom = 0.5) + custom_theme
dashed_line <- geom_hline(yintercept = 0.95, linetype = "dashed", color = "blue")
zip_plot + 
  annotate("segment", x = -Inf, xend = Inf, y = 0.95, yend = 0.95, linetype = "dashed", color = "blue") +
  dashed_line
ggsave(filename = "images/scenarioOR/zip.png")
```

@@

ggplot(melted_data, aes(x = model, y = value, fill = factor(variable, levels = c("empse", "modelse")))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  coord_flip() + # Makes the bar plots horizontal
  labs(y = "SE", x = "model", fill = "SE") +
  scale_fill_manual(
    values = c("empse" = "lightgray", "modelse" = "darkgray"), 
    labels = c("empse" = "Empirical SE", "modelse" = "Model SE")
  ) +
  custom_theme
ggsave(filename = "images/scenarioOR/secompare.png")
```
